---
title: "Unmarried men in DK"
author: "Emil B. Thomsen"
date: "27/03/2021 updated `r format(Sys.time(), '%B %d, %Y')`"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r setup, include=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=TRUE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```


## Loading the packages:
```{r}
# Library 
library(raster)
library(rgeos)
library(sf)
library(tidyverse)
library(htmltools)
library(googlesheets4)
library(mapview)
```

## HW Question

__1) test for the autocorrelation of the distribution of single women OR single men in Denmark during 2020, and answer the question: "Is the population of single women/men in Denmark spatially correlated? What is the correlation and how significant is the trend?__

<\br>
### Loading data:

```{r}
# Have to run this in order to download the spreadsheet.
gs4_deauth()

#Downloading spreadsheet
relationsship_status <- read_sheet("https://docs.google.com/spreadsheets/d/1xcrd07gV3Sm0fuzSIWu2Op36oDBmvvrlHU9uNz49kuU/edit#gid=0")


#Creating subdata set. The assignment focusses on unmarried men.
men <- subset(relationsship_status, Sex == "Mænd")
unmarried_men <- subset(men, Status == "Ugift")

#If I wish to work with the ladies.
women <- subset(relationsship_status, Sex == "Kvinder")

#checking unique number different single status.
unique(relationsship_status$Status)
```
When looking at the unique relationship statuses in the data set it can be seen that it contains 4 different types of relationship status: "unmarried", "married/separeret", "widow/widower" and "Divorced". These categories does actually not say anything about people being single. To simplify the assignment I will look at the distribution of unmarried men.

<\br>

## Creating map of DK

```{r}
#Loading data from datafolder:
mun_sp <- readRDS("data/gadm36_DNK_2_sp.rds")
mun_sf <- st_as_sf(mun_sp)
mun <- st_transform(mun_sf, crs = 32632)
mapview(mun)

sort(mun$NAME_2)
which(grepl("Å",mun$NAME_2))
which(grepl("Vest",mun$NAME_2))

mun$NAME_2[31] <- "Aarhus"
mun$NAME_2[21] <- "Høje-Taastrup"
mun$NAME_2[60] <- "Vesthimmerlands"
head(mun)
```

## Creating map of unmarried danish men

```{r}
# Creating a data frame containing the sum of all men in the different municipalities, that means the sum of men who are "Ugift", "Gift/separeret", "Enke/enkemand" or "Fraskilt".
men_sum <- men %>% 
  group_by(Region) %>% 
  summarize(sum2020 = sum(Y2020K1))


# Creating a new data frame by merging the sum DF with the unmarried_men DF. Then adding a column in the new DF with the unmarried percentage of men.
men_pct <- mun %>% 
  select(NAME_2) %>% 
  merge(unmarried_men, by.x = "NAME_2",by.y ="Region") %>% 
  merge(men_sum, by.x = "NAME_2",by.y ="Region") %>% 
  group_by(NAME_2, Status) %>% 
    mutate(pct_unmaried = Y2020K1/sum2020*100)



#Mapping the men_pct DF onto the map of DK
men_pct %>% 
  group_by(NAME_2) %>% 
  select(pct_unmaried) %>% 
  mapview()

```
Ass we can see on the map it looks like there is a spatial correlation of unmarried men in Denmark. To be sure about it a moran test can be performed:


## Defining neighbors.

```{r}
library(spdep)
# Plotting the geometry column
plot(men_pct$geometry)

#finding the neighbors of each polygon:
nb <- poly2nb(men_pct$geometry)
nb

#Finding centerpoints of each municipality
mun_centers <- st_coordinates(st_centroid(men_pct$geometry))

#plotting
plot(men_pct$geometry); plot(nb, mun_centers, col = "red",add = TRUE)

```

## Moran's I test

```{r}
options(scipen = 999)
moran.test(men_pct$pct_unmaried, 
           nb2listw(nb, style = "W",zero.policy=TRUE),
           zero.policy=TRUE)


moran.mc(men_pct$pct_unmaried,nb2listw(nb, zero.policy=TRUE),zero.policy=TRUE, nsim = 999)

```
The p-values from the moran and monte carlo are lower that the recomended 5%. more precisely in the moran test 0.6% and 0.2 procent. This means that the probability of that the distribution of umarried men in Denmark has a 0.2% of being random. that means. 
